### 2024-11-29 00_JRR-submission-folder_elsevier-latex-template_COMPLETED/cas-dc-template.tex
update

We introduce T-reX, a Python tool extending the brightway ecosystem to allow facile quantification of user-defined supply chain demands in current and prospective scenarios. T-reX streamlines database manipulation for LCA practitioners and integrates methods to aggregate and analyse waste and material flows, facilitating rapid hotspot identification.

@@

>>>>

We introduce T-reX, a Python tool extending the Brightway computational ecosystem to allow facile quantification of user-defined supply chain demands in current and prospective scenarios. T-reX streamlines database manipulation for LCA practitioners and integrates methods to aggregate and analyse waste and material flows, facilitating rapid hotspot identification.

@@

\clearpage

%% GRAPHICAL ABSTRACT
\begin{figure}[h!]
	\centering
	\includegraphics[width=\textwidth]{figs/grabs_T-reX_graphical-abstract.pdf}
	\caption{Graphical abstract of the T-reX program for waste and material footprinting in Life Cycle Assessment}
	\label{fig:graphical_abstract}
\end{figure}

\clearpage

% Switch to landscape for the included PDF
\newgeometry{landscape}
\includepdf[pages=1, width=\textheight]{figs/grabs_T-reX_graphical-abstract.pdf}
\restoregeometry % Restore the original geometry
